---
title: "twitter_analyze"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nnet)
library(nlme)
library(ggplot2)
library(dotwhisker)
library(broom)
library(tidyverse)
library(lmerTest)
library(sjPlot)
library(ggrepel)
library(car)
```



######################### Affective Content ####################################
```{r}
dfContent = read.csv("data/all_affectivecontent.csv",
                 header = TRUE)
```

All
```{r}
dfContent.All = dfContent %>% filter(type == 'All')
```
```{r}
dfContent.All$culture = factor(dfContent.All$culture, levels = c("US",'JP'))
dfContent.All$affect = factor(dfContent.All$affect, levels = c("HAN",'LAN','LAP','HAP'))
```
```{r}
plot.content = ggplot(dfContent.All,
                          aes(x = affect, y = value, fill = culture, group = culture)) +
  geom_bar(stat="identity", color="black", position=position_dodge(0.7), width=0.7) +
  scale_y_continuous(limits=c(0, 40),
                     breaks=seq(0, 40, 10)) +
  scale_fill_manual(values=c("#3b3b3b", "#bebebe")) +
  scale_x_discrete(labels=c("High Arousal\nNegative\n(HAN)", "Low Arousal\nNegative\n(LAN)", "Low Arousal\nPositive\n(LAP)", "High Arousal\nPositive\n(HAP)")) +
  ylab("Percentage of Tweets") +
  theme_bw() +
  theme(legend.position = "none",
        #axis.text.y = element_blank(),
        axis.text.y = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank()
        ) 

print(plot.content)
#ggsave("plots/newplots/allcategories_originaltweets_content.pdf", plot.content, width = 7, height = 3)
```
Pure
```{r}
dfContect.Pure = dfContent %>% filter(type == 'Pure')
```
```{r}
dfContect.Pure$culture = factor(dfContect.Pure$culture, levels = c("US",'JP'))
dfContect.Pure$affect = factor(dfContect.Pure$affect, levels = c("HAN",'LAN','LAP','HAP'))
```
```{r}
plot.content = ggplot(dfContect.Pure,
                          aes(x = affect, y = value, fill = culture, group = culture)) +
  geom_bar(stat="identity", color="black", position=position_dodge(0.7), width=0.7) +
  scale_y_continuous(limits=c(0, 40),
                     breaks=seq(0, 40, 10)) +
  scale_fill_manual(values=c("#3b3b3b", "#bebebe")) +
  scale_x_discrete(labels=c("High Arousal\nNegative\n(HAN)", "Low Arousal\nNegative\n(LAN)", "Low Arousal\nPositive\n(LAP)", "High Arousal\nPositive\n(HAP)")) +
  ylab("Percentage of Tweets") +
  xlab("Pure") +
  theme_bw() +
  theme(legend.position = "none",
        #axis.text.y = element_blank(),
        axis.text.y = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title.y = element_text(size=16),
        axis.title.x = element_text(size=16),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank()
        ) 

print(plot.content)
#ggsave("plots/newplots/allcategories_originaltweets_content_pure.pdf", plot.content, width = 7, height = 3)
```
Mixed
```{r}
dfContect.Mixed = dfContent %>% filter(type == 'Mixed')
```
```{r}
dfContect.Mixed$culture = factor(dfContect.Mixed$culture, levels = c("US",'JP'))
dfContect.Mixed$affect = factor(dfContect.Mixed$affect, levels = c("LAPHAN",'HAPHAN','LAPLAN','HAPLAN'))
```
```{r}
plot.content = ggplot(dfContect.Mixed,
                          aes(x = affect, y = value, fill = culture, group = culture)) +
  geom_bar(stat="identity", color="black", position=position_dodge(0.7), width=0.7) +
  scale_y_continuous(limits=c(0, 40),
                     breaks=seq(0, 40, 10)) +
  scale_fill_manual(values=c("#3b3b3b", "#bebebe")) +
  scale_x_discrete(labels=c("HAN-LAP", "HAN-HAP", "LAN-LAP", "LAN-HAP")) +
  ylab("Percentage of Tweets") +
  xlab("Mixed") +
  theme_bw() +
  theme(legend.position = "none",
        #axis.text.y = element_blank(),
        axis.text.y = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title.y = element_text(size=16),
        axis.title.x = element_text(size=16),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank()
        ) 

print(plot.content)
#ggsave("plots/newplots/allcategories_originaltweets_content_mixed.pdf", plot.content, width = 7.5, height = 3)
```



############################ Affective Contagion ###############################

###### Within-Culture Contagion ###########
Load and clean data
```{r}
dfUS = read.csv("data/US_within_culture_comparison.csv",
                 header = TRUE)
dfJP = read.csv("data/JP_within_culture_comparison.csv",
                 header = TRUE)
```
```{r}
dfUS = dfUS %>% 
  mutate(expoHAP = xfriendHAP*100,
         expoLAP = xfriendLAP*100,
         expoHAN = xfriendHAN*100,
         expoLAN = xfriendLAN*100,
         expoNEU = xfriendNEU*100)
dfJP = dfJP %>% 
  mutate(expoHAP = xfriendHAP*100,
         expoLAP = xfriendLAP*100,
         expoHAN = xfriendHAN*100,
         expoLAN = xfriendLAN*100,
         expoNEU = xfriendNEU*100)
```

Model and clean results to one dataframe
```{r}
model_formula = Y ~ 0 +
  dhap + dlap + dhan + dlan +
  dhap:(expoHAP + expoLAP + expoHAN + expoLAN) +
  dlap:(expoHAP + expoLAP + expoHAN + expoLAN) +
  dhan:(expoHAP + expoLAP + expoHAN + expoLAN) +
  dlan:(expoHAP + expoLAP + expoHAN + expoLAN) +
  (0 + dhap + dlap + dhan + dlan |subID)   #U
```
```{r}
# Run models
US_multivarmod = glmer(model_formula,
                    data=dfUS,
                    family=binomial(link=logit),
                    nAGQ=0,
                    control=glmerControl(optimizer = "nloptwrap"))
JP_multivarmod = glmer(model_formula,
                    data=dfJP,
                    family=binomial(link=logit),
                    nAGQ=0,
                    control=glmerControl(optimizer = "nloptwrap"))

```
```{r}
# Clean model outputs
df.US.multivarmod <- as.data.frame(tidy(US_multivarmod)) %>% 
  filter(group == 'fixed') %>%
  mutate(or = exp(estimate),
         conf.low = exp(estimate-1.96*std.error),
         conf.high = exp(estimate+1.96*std.error)) %>% 
  filter(term=='dlan:expoLAN' |
         term=='dhan:expoHAN' |
         term=='dlap:expoLAP' |
         term=='dhap:expoHAP') %>% 
  mutate(term = recode_factor(term, 'dhan:expoHAN'='HAN', 'dlan:expoLAN'='LAN', 
                              'dlap:expoLAP'='LAP', 'dhap:expoHAP'='HAP')) %>% 
  select(-c(estimate, std.error)) %>% 
  mutate(estimate = or)

df.JP.multivarmod <- as.data.frame(tidy(JP_multivarmod)) %>% 
  filter(group == 'fixed') %>%
  mutate(or = exp(estimate),
         conf.low = exp(estimate-1.96*std.error),
         conf.high = exp(estimate+1.96*std.error)) %>% 
  filter(term=='dlan:expoLAN' |
         term=='dhan:expoHAN' |
         term=='dlap:expoLAP' |
         term=='dhap:expoHAP') %>% 
  mutate(term = recode_factor(term, 'dhan:expoHAN'='HAN', 'dlan:expoLAN'='LAN', 
                              'dlap:expoLAP'='LAP', 'dhap:expoHAP'='HAP')) %>% 
  select(-c(estimate, std.error)) %>% 
  mutate(estimate = or)
```
```{r}
# Combine outputs of both cultures
culture = c('US', 'US', 'US', 'US', 'JP', 'JP', 'JP', 'JP')
colors = c("black", "black", "black", "black", "grey41", "grey41", "grey41", "grey41")
df.both.multivarmod = rbind(df.US.multivarmod, df.JP.multivarmod)
df.both.multivarmod$"culture" = culture
df.both.multivarmod$"colors" = colors

df.both.multivarmod = df.both.multivarmod %>% 
  mutate(affect = term) %>% 
  select(-c(term))

df.both.multivarmod$culture = factor(df.both.multivarmod$culture, levels = c("US",'JP'))
df.both.multivarmod$affect = factor(df.both.multivarmod$affect, levels = c("HAN",'LAN','LAP','HAP'))
```

Plot
```{r}
plot.multivarmod = ggplot(df.both.multivarmod,
                          aes(x = affect, y = or-1, fill = culture, group = culture)) +
  geom_bar(stat="identity", color="black", position=position_dodge(0.7), width=0.7) +
  geom_errorbar(aes(ymin=conf.low-1, ymax=conf.high-1), position=position_dodge(0.7), width=.1) +
  scale_y_continuous(limits=c(0.00,0.045),
                     breaks=seq(0.00, 0.045, 0.01),
                     labels = function(y) y + 1) +
  scale_fill_manual(values=c("#3b3b3b", "#bebebe"), labels = c("United States", "Japan")) +
  scale_x_discrete(labels=c("High Arousal\nNegative\n(HAN)", "Low Arousal\nNegative\n(LAN)", "Low Arousal\nPositive\n(LAP)", "High Arousal\nPositive\n(HAP)")) +
  ylab("Contagiousness") +
  theme_bw() +
  theme(legend.position = "none",
        #axis.text.y = element_blank(),
        axis.text.y = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank()
        ) 

print(plot.multivarmod)
#ggsave("plots/newplots/allcategories_originaltweets_contagion.pdf", plot.multivarmod, width = 7, height = 3)
```

Stats to compare coefficients
```{r}
linearHypothesis(JP_multivarmod, "dlan:expoLAN = dhap:expoHAP")
```



###### Between-Culture Contagion ###########
Load data
```{r}
dfAllBetCult = read.csv("data/between_culture_comparison.csv",
                 header = TRUE)
```
Run models
```{r}
betculthapmod = glmer(formula=HAP ~ 1 + 
                        friendHAP*culture + 
                        friendLAP*culture + 
                        friendLAN*culture + 
                        friendHAN*culture + 
                        (1|subID), 
                data=dfAllBetCult,
               family=binomial,
               nAGQ=0,
               control=glmerControl(optimizer = "nloptwrap"))
betcultlapmod = glmer(formula=LAP ~ 1 + 
                        friendHAP*culture + 
                        friendLAP*culture + 
                        friendLAN*culture + 
                        friendHAN*culture + 
                        (1|subID), 
                data=dfAllBetCult,
               family=binomial,
               nAGQ=0,
               control=glmerControl(optimizer = "nloptwrap"))
betculthanmod = glmer(formula=HAN ~ 1 + 
                        friendHAP*culture + 
                        friendLAP*culture + 
                        friendLAN*culture + 
                        friendHAN*culture + 
                        (1|subID), 
                data=dfAllBetCult,
               family=binomial,
               nAGQ=0,
               control=glmerControl(optimizer = "nloptwrap"))
betcultlanmod = glmer(formula=LAN ~ 1 + 
                        friendHAP*culture + 
                        friendLAP*culture + 
                        friendLAN*culture + 
                        friendHAN*culture + 
                        (1|subID), 
                data=dfAllBetCult,
               family=binomial,
               nAGQ=0,
               control=glmerControl(optimizer = "nloptwrap"))
```
Clean model outputs and combine to one dataframe
```{r}
btcultmodhapfilter <- broom::tidy(betculthapmod) %>% 
  filter(group == 'fixed') %>% 
  mutate(or = exp(estimate),
         conf.low = exp(estimate-1.96*std.error),
         conf.high = exp(estimate+1.96*std.error)) %>% 
  filter(term=='friendHAP:culture')

btcultmodlapfilter <- broom::tidy(betcultlapmod) %>% 
  filter(group == 'fixed') %>% 
  mutate(or = exp(estimate),
         conf.low = exp(estimate-1.96*std.error),
         conf.high = exp(estimate+1.96*std.error)) %>% 
  filter(term=='culture:friendLAP')

btcultmodhanfilter <- broom::tidy(betculthanmod) %>% 
  filter(group == 'fixed') %>% 
  mutate(or = exp(estimate),
         conf.low = exp(estimate-1.96*std.error),
         conf.high = exp(estimate+1.96*std.error)) %>% 
  filter(term=='culture:friendHAN')

btcultmodlanfilter <- broom::tidy(betcultlanmod) %>% 
  filter(group == 'fixed') %>%
  mutate(or = exp(estimate),
         conf.low = exp(estimate-1.96*std.error),
         conf.high = exp(estimate+1.96*std.error)) %>% 
  filter(term=='culture:friendLAN')


btcultmodfilter = rbind_list(list(btcultmodhapfilter,
                                  btcultmodlapfilter,
                                  btcultmodlanfilter,
                                  btcultmodhanfilter)) %>% 
  mutate(term = recode_factor(term, 'culture:friendHAN'='HAN', 'culture:friendLAN'='LAN',
                              'culture:friendLAP'='LAP', 'friendHAP:culture'='HAP')) %>% 
  select(-c(estimate, std.error)) %>% 
  mutate(estimate = or)
```


####################### Contagion vs. Content ##################################
Join contagion and content dataframes
```{r}
df.contagion.content = inner_join(dfContent.All, df.both.multivarmod, by=c("culture", "affect"))
df.contagion.content = df.contagion.content %>% 
  select(c(affect, culture, value, or)) %>% 
  rename(content = value) %>% 
  rename(contagion = or)
```
Plot
```{r}
plot.contentcontagion = ggplot(df.contagion.content,
                               aes(x = content, y = contagion, label=affect, 
                                   group = culture,
                                   fill = culture,
                                   color=culture)) + 
  geom_point(size=2.5) +
  geom_label_repel(box.padding = 0.35, 
                  point.padding = 0.4,
                  segment.color = 'black',
                  label.size = NA, 
                  color = "white") +
  scale_x_continuous(limits=c(0, 40),
                     breaks=seq(0, 40, 10)) +
  scale_y_continuous(limits=c(1.00,1.045),
                     breaks=seq(1.00, 1.045, 0.01)) +
  scale_fill_manual(values=c("#3b3b3b", "#bebebe"), 
                    labels = c("United States", "Japan")) +
  scale_color_manual(values=c("#3b3b3b", "#bebebe"), 
                    labels = c("United States", "Japan")) +
  #scale_fill_manual(values=c("white", "white"), labels = c("United States", "Japan")) +
  ylab("Affective contagion (contagiousness)") +
  xlab("Affective content (percentage of original tweets)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=10),
        axis.title.y = element_text(size=11),
        axis.title.x = element_text(size=11),
        strip.text.x = element_text(size=16)
        #panel.grid.major = element_blank(), 
        #panel.grid.minor = element_blank(),
        ) 

print(plot.contentcontagion)
#ggsave("plots/newplots/originaltweets_contagion_vs_content.pdf", plot.contentcontagion, width = 4, height = 5)
```

Correlation test for contagion vs. content
```{r}
cor.test(df.contagion.content$content,df.contagion.content$contagion,method="spearman", alternative="two.sided")
```

